\chapter{Introduction}
\label{chap:introduction}
This chapter will explain the purpose of this document as well as what the scope of this document is. That is, what the purpose of this document is and how it is related to other documents in the project.

\section{Purpose}
The purpose of this document is to set rules and guidelines to which all project members should adhere. This will concern the versioning, identification and layout of all documents that are created for this project. All major documents should adhere to strict rules, while for other documents, such as files containing code, guidelines are set that are more loose.

This document should be read as a reference. It can be used when a developer or project member is not sure about how to do something as a mainstay.

\section{Scope}
In this project, the following configuration items (CIs) will be produced:
\begin{itemize}
	\item Architectural Design Document (ADD);
	\item Detailed Design Document (DDD);
	\item Software Configuration Management Plan (SCMP);
	\item Software Project Management Plan (SPMP);
	\item Software Quality Assurance Plan (SQAP);
	\item Software Requirements Document (SRD);
	\item Software Transfer Document (STD);
	\item Software User Manual (SUM);
	\item Software Verification and Validation Plan (SVVP);
	\item User Requirements Document (URD);
	\item Code;
	\item Test plans for a number of phases. In particular:
	\begin{itemize}
		\item Unit Test Plan (UTP);
		\item Integration Test Plan (ITP);
		\item Acceptance Test Plan (ATP).
	\end{itemize}
	\item Product Backlog.
\end{itemize}
The ESA standard mentions a System Test Plan (STP) as well, but in our case this can be omitted.

\section{List of definitions}
\begin{tabular}{@{}ll@{}}
	\toprule
	2IP35 & The Software Engineering Project \\
	ADD   & Architectural Design Document \\
	ATP   & Acceptance Test Plan \\
	BCF   & Bureau for Computer Facilities \\
	CI    & Configuration Item \\
	CM    & Configuration Manager \\
	DDD   & Detailed Design Document \\
	ITP   & Integration Test Plan \\
	SEP   & Software Engineering Project \\
	SCMP  & Software Configuration Management Plan \\
	SPMP  & Software Project Management Plan \\
	SQAP  & Software Quality Assurance Plan \\
	SRD   & Software Requirements Document \\
	STD   & Software Transfer Document \\
	STP   & System Test Plan \\
	SUM   & Software User Manual \\
	SVVP  & Software Verification and Validation Plan \\
	TU/e  & Eindhoven University of Technology \\
	URD   & User Requirements Document \\
	UTP   & Unit Test Plan \\
	\bottomrule
\end{tabular}

\section{List of references}
\bibliographystyle{plain}

\bibliography{../ref}