\chapter{Introduction}\label{chap:intro}
%\label{chap:intro}
This chapter lists general information about this document.

\section{Purpose}
The UTP document describes the plan for testing the developed software units against the
detailed design, defined in the DDD \cite{DDD}. The unit tests make sure that \projectname\ complies
with the design in the Detailed Design (DD) phase of \projectname\ as described in
the ESA software engineering standard \cite{esa}.

\section{Overview}
\label{sec:overview}

Chapter \ref{chap:testPlan} gives an overview of all items that will be tested, and the general criteria for the UT.
Chapter \ref{chap:testcasespec} speciﬁes how tests are defined, chapter \ref{chap:testProc} specifies the test procedures and chapter \ref{chap:testReports} speciﬁes how test results are reported.


\section{List of definitions and abbreviations}
\label{sec:listofdef}


\subsection{Definitions}
\label{subsec:def}

\todo{Check if this list again after chapter 5 has been written. At the moment Firefox, Chrome, IE, iOS, iOS Safari, Safari,
Opera, System Administrator don't appear in the document and can be deleted from this list.}

\begin{description}
%TODO: checken of deze begrippen daadwerkelijk gebruikt worden en aanvullen met nieuwe begrippen.


\item[Client] Prof.dr.ir. P.D. Anderson.
\item[Firefox] A web browser developed by Mozilla.
\item[Google Chrome] A web browser developed by Google.
\item[GWT] A Java software development toolkit by Google for building and optimizing browser-based applications.
\item[Internet Explorer] A web browser developed by Microsoft.
\item[iOS] A mobile operating system developed by Apple.
\item[iOS Safari] A web browser developed by Apple designed for devices running iOS.
\item[iPhone] A line of smartphones developed by Apple.
\item[iPad] A line of tablet computers developed by Apple.
\item[Opera] A web browser developed by Opera Software.
\item[Safari] A web browser developed by Apple.
\item[System administrator] A person who is employed to maintain and operate a computer system and/or network. After the SEP project has been completed, this person will be responsible for maintaining the \applicationname{}.
\item[Selenium] Tool to automate browser input.
\item[Ant] Tool to build Java applications.
\item[JUnit] A unit testing framework for the Java programming language.
\item[Eclipse] A universal toolset for software development.
\end{description}

\subsection{Abbreviations}
%\label{subsec:abbrev}
%TODO: checken of al deze afkortingen daadwerkelijk gebruikt worden en aanvullen met nieuwe afkortingen.
\begin{tabular}{l|l}
2IP35 & The Software Engineering Project \\
ADD & Architectural Design Document \\
CM    & Configuration Manager \\
GUI & Graphical User Interface \\
SEP   & Software Engineering Project \\
SR    & Software Requirements \\
SRD   & Software Requirements Document \\
TU/e  & Eindhoven University of Technology \\
URD   & User Requirements Document \\
JDK   & Java Development Kit \\
GWT   & Google Web Toolkit \\
UT    & Unit Test
\end{tabular}

\section{List of references}
\bibliography{../ref}
