\chapter{ITP feedback}\label{chap:itp-feedback}

\section{Chapter 1}
\subsection{Internal reviews}
\feedbackTableStart{\femke{}}{0.0}
1.2 & Other & You mention here that chapter 3 gives a detailed description of the test cases, but in my opinion, the given description is very brief. Either remove ``detailed'' here or make chapter 3 more detailed. \\
\end{longtable}

\section{Chapter 2}
\subsection{Internal reviews}
\feedbackTableStart{\benjamin{}}{0.0}
2 & Other & \emph{3-5} would look better as \emph{3 to 5}. \\
2.2 & Question & This subsection is unclear. What does it matter and why does this mean all features are tested with ITs? \\
2.3 & Other & Change \emph{documents/code} to \emph{items}, characters like the slash look messy. \\
2.3 & Other & Inconsistent `.'ing in the list. \\
2.5 & Other & Change \emph{hardware/software} to \emph{hardware and software}. \\
\end{longtable}

\feedbackTableStart{\femke{}}{0.0}
2 & Incorrect & This introductory text is not suited for the ITP, as it is about ``acceptance tests''. I would also slightly rephrase this sentence, for instance: ``This chapter describes what items are tested with integration tests and how these items must be tested.'' \\
2.1 & Other & Perhaps you can also mention here that the components are from chapter 5 of the ADD. I think that would clarify about which components you're talking here. \\
2.1 & Other & See previous remark: if you include the reference to chapter 5, perhaps you can also list the components in the same order here as in chapter 5 of the ADD. \\
2.3 & Style & I would rephrase the last sentence of this section to ``After the tests are concluded, test reports should be written. Problem reports should be written when necessary.'' This makes it also consistent with the text in the ATP. \\
2.4 & Question & What do you mean with ``Integration test input data needs to be created''? What is this ``input data''? \\
2.5 & Incorrect & This section is about running the application, but it should discuss ``properties required of the test environment''. \\
2.6 & Incorrect & The test criteria are not described in chapter 3. In chapter 3, you describe the test cases. \\
\end{longtable}

\feedbackTableStart{\hugo{}}{0.0}
2.2 & 		Remark & 	I don't think this sentence gives the information you expect in the section ``features to be tested''\\
2.3 & 		Other & 	``..the test reports (chapter 5).'' I would replace it with ``chapters 1-4'' to prevent confusion about incl or excl chapter 5. \\
2.6 & 		Other & 	``Similarly'' implies 'all things have to pass as well'. It's not the right word in this context.\\
\end{longtable}

\section{Chapter 3}
\subsection{Internal reviews}
\feedbackTableStart{\benjamin{}}{0.0}
3 & Missing & The link to a figure in the ADD is broken (it says figure \textbf{??}). \\
\end{longtable}

\section{Chapter 4}
\subsection{Internal reviews}
\feedbackTableStart{\benjamin{}}{0.0}
4 & Missing & The link to a chapter in the UTP is broken (it says chapter \textbf{??}). \\
\end{longtable}

\section{Chapter 5}
\subsection{Internal reviews}
\feedbackTableStart{\femke{}}{0.0}
5 & Missing & Perhaps you can say what the listed items are the individual tests from the mentioned test classes. Providing information in a tabular format might also clarify things even more. \\
5 & Missing & According to the general info document, you should also include ``when was the test performed, by who and who witnessed it. \\
\end{longtable}
