\chapter{SUM Feedback}
\label{chap:sum-feedback}

% Abstract --------------------------------------------------------------------------------------------------------------------------------
\section{Abstract}
\subsection{Internal reviews}
\feedbackTableStart{\roel}{0.0}
abstract & Typo & Broken references to the ESA. \\
\end{longtable}

\feedbackTableStart{\benjamin{}}{0.0}
General & Typo & There are a lot of cases where the Fingerpaint application is referenced, but these are not followed by spaces (e.g. The Fingerpaint applicationis awesome). \\
General & Typo & Closing quotes '' are used to open a quote. These should be `` instead. \\
Abstract & Other & It is unclear what is meant by \emph{This program}. \\
\end{longtable}

% Chapter 1 --------------------------------------------------------------------------------------------------------------------------------
\section{Chapter 1}
\subsection{Internal reviews}
\feedbackTableStart{\roel}{0.0}
1.7 & Question & It is stated that problems cannot be reported at group fingerpaint. However, the chapter
does not state where problems can be reported. \\
\end{longtable}

\feedbackTableStart{\benjamin{}}{0.0}
1.1 & Other & Insert a comma in \emph{\ldots mobile device basic knowledge \ldots} (fixed). \\
1.6 & Other & Change \emph{italic text} to \emph{italics} for consistency (fixed). \\
1.6 & Other & This line runs off the page (fixed). \\
1.7 & Other & Change \emph{\ldots the Group Fingerpaintwill \ldots} to \emph{\ldots Group Fingerpaint will \ldots} (fixed). \\
\end{longtable}

% Chapter 2 --------------------------------------------------------------------------------------------------------------------------------
\section{Chapter 2}
\subsection{Internal reviews}
\feedbackTableStart{\roel}{0.0}
2.0 & Typo & On the first line, there is no space behind Fingerpaint. \\
\end{longtable}

% Chapter 3 --------------------------------------------------------------------------------------------------------------------------------
\section{Chapter 3}
\subsection{Internal reviews}
\feedbackTableStart{\roel}{0.0}
3.3.3 & Typo & In results, wall movement should be plural. \\
3.4.1 & Structure & The description is about a mixing protocol, while the section is only about a single
step. \\
3.5 \& 3.6 & Structure & Why are the exporting functions described before the corresponding viewing
functions. \\
3.8 & Missing & Missing pictures of the loading menu. \\
3.11 & Missing & Missing pictures of the removing menu. \\
3.17.4 & Typo & Broken reference. \\
3.* & Question & Possible errors is oftentimes empty because the error message is described in
cautions. (occurs in chapter 4 as well) I would mention the error a second time. A good example is 4.1. \\
\end{longtable}

\feedbackTableStart{\benjamin{}}{0.0}
3.* & Other & It might be better to change the `X' used for indicating the \texttt{Toggle Menu} button to $\times$. \\
3.* & Other & There are forward references in some tutorials. The \emph{Remove some item} tutorials in particular contain forward references to \emph{Save some item} tutorials. \\
3.* & Other & Some references are broken. \\
3.1.2, 3.1.3 & Other & Inconsistent `.' at the end of enumerations (fixed). \\
3.1.4 & Other & Remove the colon after the error message, as it does not end the sentence (fixed). \\
3.2.4 & Other & Do not use \emph{can't}', but use \emph{cannot} (fixed). \\
3.3.3 & Other & Superfluous \emph{to} in \emph{\ldots can to be used \ldots} (twice) (fixed). \\
3.3.3 & Other & \emph{When the protocol is satisfactory \ldots} sounds strange. \\
3.4.1 & Other & This refers to \emph{\ldots the mixing protocol \ldots} which implies there is only one protocol possible. \\
3.4.3 & Other & \emph{\ldots right away} sounds very informal. \\
3.5.2 & Other & \emph{\ldots after \textbf{a} successful mixing run \ldots} (fixed). \\
3.5.2 & Other & \emph{\ldots after \textbf{a} single step simulations} (fixed). \\
3.5.2 & Other & \emph{Hence exporting is not possible} is a fragment (fixed). \\
3.5.3, 3.6.3, 3.7.3 & Other & Try to avoid characters like `/', use \emph{or} instead. \\
3.6.3 & Other & Spell out small numbers like \emph{2}. \\
3.6.3 & Other & Change \emph{\ldots of the selected mixing runs appears 3.5} to \emph{\ldots of the selected mixing runs appears (figure 3.5)} (fixed). \\
3.14.2 & Incorrect & One can simply save the white distribution without explicitly defining it as such. \\
3.17.3, 3.18.3 & Other & Typeset the x and y of \emph{x-axis} in mathmode ($x$-axis). \\
3.17.3 & Other & \emph{\ldots the mixing performance from the mixing results are displayed} contains a singular noun as subject and a plural verb. \\
\end{longtable}

% Chapter 4 --------------------------------------------------------------------------------------------------------------------------------
\section{Chapter 4}
\subsection{Internal reviews}
\feedbackTableStart{\roel}{0.0}
4.* & Other & Spinner is mentioned multiple times in the chapter (e.g. 4.3). I don't think spinner is a
term known by non-developers. \\
4.5 & Other & Saying the load and remove button have reduced funtionality sound weird. It should be
stated more specifically that files cannot be deleted/loaded if there are no files to
delete/load. \\
4.7 & Structure & You should state more specifically that using the Step Size spinner affects the step size
of NEW mixing steps in the Functional description. \\
4.9 & Incorrect & Formal description: Remove part of a file name does not always work this way, because the
cursor can be placed in the middle of the name, instead of at the end. \\
\end{longtable}

\feedbackTableStart{\hugo}{0.0}
4.x & 		Inconsistent & 	textdt{} is used for buttons and emph{} for menu's. In the rest of the document emph{} is used for both.\\
4.x & 		Other & 	Maybe some picture would be illustrative.\\
4.1 & 		Other & 	\emph{Cell browser} is a technical term for 'a menu'. In the user manual the reader shouldn't be confronted with such terminology.\\
4.1 & 		Other & 	idem for \emph{level}. I suggest to change it to \emph{column} or \emph{drop-down menu} (drop-right menu).\\
4.2 &		Typo & 		\emph{The drawing area is used for drawing the initial concentration result.} 'initial concentration result' $\rightarrow$ \emph{concentration distribution}. You don't draw a result. \\
4.3 & 		Other & 	\emph{spinner} is a technical term for 'a menu where you specify a value'. In the user manual the reader shouldn't be confronted with such terminology. I don't know if this issue is resolved by the glossary...\\
4.5 & 		Other & 	\emph{the user can choose to overwrite that name} You overwrite the file, not the name.\\
4.5 & 		Typo & 		\emph{If there are more results than fit on the screen} Insert 'can'. Also the cellList is limited to x-pixels (hardcoded value), not the fullscreen. So technically it's not true. (idem for other cellLists in the document)\\
4.9 & 		Typo & 		\emph{only possible with a new of}. new $\rightarrow$ name.\\
\end{longtable}


% Appendix A ------------------------------------------------------------------------------------------------------------------------------
\section{Appendix A}
\subsection{Internal Reviews}
\feedbackTableStart{\benjamin{}}{0.0}
A.* & Other & The header of this appendix is too long and does not fit next to \emph{Fingerpaint}. \\
A.1.1 & Other & \emph{There are two specific cases in which this error might occur. Firstly, when trying to load the application. Secondly, when trying to execute a mixing run.}
These lines are fragmentary and should be combined into one sentence. \\
A.1.2 & Other & \emph{throws an error} might sound strange to non-computer scientists. \\
A.2.1 & Other & \emph{\ldots a new name can be specified to save the specified item} sounds strange, it might be better to change the second \emph{specified} to \emph{selected} or something similar. \\
A.2.2 & Other & The suggested fix for a full storage message is to remove an item of the same type, but as local storage is site specific, removing a different item also works, as long as enough space is freed. \\
A.2.2 & Other & Incorrect tense in \emph{\ldots when this message is shown when a distribution is saved \ldots}. When something \emph{is saved}, it implies that the save was successful, but the point of this error is to notify the user that it was not. \\
A.2.3 & Other & \emph{More specifically, this error could occur \ldots} First you say \emph{more specifically}, and then \emph{could}, which is not exactly specific. \\
A.2.4 & Other & Most errors are shown when an exception occurs, and this is not interesting to the end-user. Also, the definition of error (technically failure but anyway) basically says they should not occur. The important thing is that something went wrong, and it is not any of the other errors described before. Worded as it is now, it sounds confusing. \\
A.3.1 & Other & \emph{doesn't} should be \emph{does not}. \\
A.3.1 & Other & \emph{Hereafter} sounds strange. It is probably correct though. \\
\end{longtable}

\feedbackTableStart{\hugo}{0.0}
Appendix A & 	Question &	Can we make a table of contents for the appendix? It seems useful looking at the amount of different sections/messages.\\
Appendix A.2 &	Other & 	Specifiy an \emph{item} to be either a distribution, porotocol or mxixing run at the beginning of the section rather than putting it between brackets in every subsection.\\
Appendix A.2-ish & Other & 	\emph{FINGAEPRPPEANINDTIX A. ERROR MESSAGES AND RECOVERY PROCEDURES} The header of the page has overlapping words because it is too long.\\
\end{longtable}

% Appendix B ------------------------------------------------------------------------------------------------------------------------------
\section{Appendix B}
\subsection{Internal reviews}
\feedbackTableStart{\roel}{0.0}
Appendix B & Inconsistent & The definition of mixer is inappropriate and does not fit in with the explanation
of geometry. \\
\end{longtable}

