\chapter{Introduction}
\label{chap:intro}
This chapter lists general information about this document.

\section{Purpose}
\label{sec:purpose}
The Acceptance Test Plan (ATP) describes the plan for testing \projectname{} against the user requirements as described in the URD \cite{urd}. The acceptance tests make sure that
\projectname{} complies with the requirements in the URD \cite{urd}. Therefore this document needs to be agreed upon by \projectauthor{} and the client, prof.dr.ir. P.D. Anderson.
These tests should be executed in the Acceptance Test (AT) phase of the \projectname{} project, as described in the ESA Software Engineering Standard \cite{esa}.

\section{Overview}
\label{sec:overview}
Chapter \ref{chap:testPlan} mentions the items to be tested together with the general criteria for the AT. A detailed specification for each test case is given in chapter \ref{chap:testCaseSpecs}. The procedures for the execution of the tests are explained in chapter \ref{chap:testProcedures}. After execution of the tests, reports on the results will be presented in chapter \ref{chap:testReports}.
%Todo: Add reference to Appendix A, instead of hard-coded name.
Appendix A contains a step-by-step user manual for the server setup. The client needs to perform all steps in this manual before executing the Acceptance Tests.

\section{List of definitions and abbreviations}
\label{sec:listofdef}

\subsection{Definitions}
\label{subsec:def}

\begin{description}
\item[Client] Prof.dr.ir. P.D. Anderson.
\end{description}

\subsection{Abbreviations}
\label{subsec:abbrev}
\begin{tabular}{l|l}
2IP35 & The Software Engineering Project \\
AT & Acceptance Test(s) \\
ATP & Acceptance Test Plan \\
CPR & Capability Requirement \\
ESA & European Space Agency \\
SEP   & Software Engineering Project \\
URD   & User Requirements Document \\
\end{tabular}

\section{List of references}
\bibliography{../ref}