\chapter{Introduction}

\section{Purpose}
   This document describes procedures concerning the testing of the delivered products (product
   documents and software) of the \projectname{} project for compliance with the requirements. The
   requirements that the software has to be verified against can be found in the product documents
   URD \cite{urd}, Product Backlog \cite{backlog}, SRD \cite{srd}, ADD \cite{add} and DDD \cite{ddd}. The modules to be verified and validated are defined
   in the AD phase. The goal of verifying and validating is to check whether the software product to
   be delivered conforms to the requirements of the client and to ensure a minimal number of errors
   in the software. This project document is written for managers and developers of the \projectname{}
   project.

\section{Scope}
The \applicationname{} is an application designed and developed by \projectauthor{} for Prof.dr.ir. P.D. Anderson. The first goal of the \applicationname{} is to provide an intuitive and modern interface for an already existing mixing program. This existing mixing program can calculate how the concentration distribution of a certain mixture changes as the mixer mixes. The second goal of the \applicationname{} is is to provide this service to devices unable to handle the computational load themselves. To this end, the main computation done by the existing mixing program is done on a server. These two goals are formulated as a set of formal requirements in the  URD \cite{urd}.

\section{List of definitions}
\begin{longtable}{l|l}
2IP35 & The Software Engineering Project \\ 
AD    &Architectural Design \\ 
ADD   &Architectural Design Document \\ 
%AT    &Acceptance Test \\ 
ATP   &Acceptance Test Plan \\ 
Client &Prof.dr.ir. P.D. Anderson \\ 
%CM    &Configuration Manager \\ 
CI &Configuration Item\\
DD    &Detailed Design \\ 
DDD   &Detailed Design Document \\ 
ESA   &European Space Agency \\ 
%TU/e  &Eindhoven University of Technology \\ 
%OM    &Operations and Maintenance Plan \\ 
PM    &Project Manager \\ 
QAM &Quality Assurance Manager\\
SCMP  &Software Configuration Management Plan \\ 
SEP   &Software Engineering Project \\ 
%SL    &Software Librarian \\ 
SM	  &Senior Management \\
SPMP  &Software Project Management Plan \\ 
SQAP  &Software Quality Assurance Plan \\ 
%SR    &Software Requirements \\ 
SRD   &Software Requirements Document \\ 
%STD   &Software Transfer Document \\ 
SUM   &Software User Manual \\ 
%SVVP  &Software Verification and Validation Plan \\ 
SVVR  &Software Verification and Validation Report \\ 
%TR    &Transfer phase \\ 
UR    &User Requirements \\ 
URD   &User Requirements Document \\ 
%VPM   &Vice Project Manager \\ 
\end{longtable}

\section{List of references}

\bibliographystyle{plainnat}
\bibliography{../ref}
