\chapter{Introduction}
\label{chap:intro}
This chapter lists general information about this document.

\section{Purpose}
\label{sec:purpose}
The Integration Test Plan (ITP) describes the plan for testing the integrated software against the architectural design, defined in the ADD \cite{add}. The integration tests make sure that
\projectname{} complies with the design in the Detailed Design (DD) phase of the \projectname{} project as described in the ESA Software Engineering Standard \cite{esa}.

\section{Overview}
\label{sec:overview}
Chapter \ref{chap:testPlan} mentions the items to be tested together with the general criteria for the IT. A detailed specification for each test case is given in chapter \ref{chap:testCaseSpecs}. The procedures for the execution of the tests are explained in chapter \ref{chap:testProcedures}. After execution of the tests, reports on the results will be presented in chapter \ref{chap:testReports}.

\section{List of definitions and abbreviations}
\label{sec:listofdef}

\subsection{Definitions}
\label{subsec:def}

\begin{description}
\item[Client] Prof.dr.ir. P.D. Anderson.
\item[Firefox] A web browser developed by Mozilla.
\item[Google Chrome] A web browser developed by Google.
\item[Internet Explorer] A web browser developed by Microsoft.
\item[iOS] A mobile operating system developed by Apple.
\item[iOS Safari] A web browser developed by Apple designed for devices running iOS.
\item[iPhone] A line of smartphones developed by Apple.
\item[iPad] A line of tablet computers developed by Apple.
\item[Opera] A web browser developed by Opera Software.
\item[Safari] A web browser developed by Apple.
\item[System administrator] A person who is employed to maintain and operate a computer system and/or network. After the SEP project has been completed, this person will be responsible for maintaining the \applicationname{}.
\end{description}

\todo{Check whether all of these definitions are still used/definitions are missing}

\subsection{Abbreviations}
\label{subsec:abbrev}
\begin{tabular}{l|l}
2IP35 & The Software Engineering Project \\
ADD & Architectural Design Document \\
CM    & Configuration Manager \\
DDD & Detailed Design Document \\
ESA & European Space Agency \\
GUI & Graphical User Interface \\
IT & Integration Test(s) \\
ITP & Integration Test Plan \\
SEP   & Software Engineering Project \\
SR    & Software Requirements \\
SRD   & Software Requirements Document \\
TU/e  & Eindhoven University of Technology \\
URD   & User Requirements Document \\
\end{tabular}

\todo{Check whether all of these Abbreviations are still used/abbreviations are missing}

\section{List of references}
\bibliography{../ref}